AAAI Press Formatting Instructions \\for Authors Using \LaTeX{} --- A Guide

### 2021-09-18 publications/iaai21/dora_outlier_detection_iaai.tex
removed my TODO flag; removed italics around z-band to just around z-
added des precision numbers to tab:faw_results
added DES combined plot

\subsubsection{Astrophysics: objects in Dark Energy Survey.}
\todo{Umaa}

@@

We used publicly-available photometry from the $g-$, $r-$, $i-$ and $z-band$ DES exposures.  We
transformed the photometry into luptitudes\footnote{A
  ``Luptitude''~\cite{lupton99} is an arcsinh-scaled flux, with
  properties quantitatively equal to
  traditional astronomical magnitudes for bright sources, but which
  gracefully handles non-detections and negative fluxes.}.  The inputs features used
  were the $r$-band luptitude, colors computed as band differences between
$g-r$, $i-r$, and $z-r$, and associated observational errors, for a total of eight features.
%

@@

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications and F-MNIST
   benchmark; the best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|cccc}
    \hline
    Algorithm & Astro. & Earth & Planetary & F-MNIST \\
    \hline
    PCA               & & 0.41 & 0.44 & \textbf{0.84} \\
    DEMUD             & & 0.41 & 0.44 & \textbf{0.84} \\
    \hline
    RX                & & 0.43 & ---- & 0.82 \\
    LRX               & & ---- & 0.33 & 0.56 \\
    \hline
    Iso. Forest  & & 0.46 & \textbf{0.56} & 0.74 \\
    \hline
    PAE               & & 0.41 & 0.44 & 0.83 \\
    Neg. Sampling & & \textbf{0.49} & 0.33 & 0.43 \\
    \hline
    Random            & & 0.32 & 0.14 & 0.49 \\
    \hline
  \end{tabular}
\end{table}

>>>>

\subsubsection{Astrophysics: objects in Dark Energy Survey.}

@@

We used publicly-available photometry from the $g-$, $r-$, $i-$ and $z-$band DES exposures.  We
transformed the photometry into luptitudes\footnote{A
  ``Luptitude''~\cite{lupton99} is an arcsinh-scaled flux, with
  properties quantitatively equal to
  traditional astronomical magnitudes for bright sources, but which
  gracefully handles non-detections and negative fluxes.}.  The inputs features used
  were the $r$-band luptitude, colors computed as band differences between
$g-r$, $i-r$, and $z-r$, and associated observational errors, for a total of eight features.
%

@@

\begin{table}
  \caption{Precision at $N=n_{outlier}$ for three applications and F-MNIST
   benchmark; the best result for each data set is in bold.}
  \label{tab:faw_results}
  \centering
  \begin{tabular}{l|cccc}
    \hline
    Algorithm & Astro. & Earth & Planetary & F-MNIST \\
    \hline
    PCA               & \textbf{0.42} & 0.41 & 0.44 & \textbf{0.84} \\
    DEMUD             & ---- & 0.41 & 0.44 & \textbf{0.84} \\
    \hline
    RX                & 0.40 & 0.43 & ---- & 0.82 \\
    LRX               & ----& ---- & 0.33 & 0.56 \\
    \hline
    Iso. Forest  & 0.34 & 0.46 & \textbf{0.56} & 0.74 \\
    \hline
    PAE               & 0.35 & 0.41 & 0.44 & 0.83 \\
    Neg. Sampling & 0.32 & \textbf{0.49} & 0.33 & 0.43 \\
    \hline
    Random            & 0.26 & 0.32 & 0.14 & 0.49 \\
    \hline
  \end{tabular}
\end{table}

\begin{figure}
    \centering
    \includegraphics[width=\linewidth]{figures/des_combined_plot.pdf}
    \caption{Number of true outliers ranked in top $N$ selections for 
    the astrophysics (DES) dataset.}
    \label{fig:des_results}
\end{figure}
